---
title: "APdata_analysisMW"
author: "Maggie Westerland"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(gtsummary)
library(skimr)
library(DBI)
library(RSQLite)
library(lubridate)
library(glmnet)
setwd('~/Desktop/grad/capstone/code')
```


```{r}
load('final_df.Rdata')
```

```{r}
final_df <- final_df %>% 
  mutate(pre_htn = as.factor(pre_htn)) %>% 
  mutate(post_htn = as.factor(post_htn)) %>% 
  mutate(bmi_return = as.factor(bmi_return)) %>% 
  mutate(gest_age_wks = as.numeric(gest_age_wks)) %>% 
  mutate(ob_gravidity = as.character(ob_gravidity)) %>% 
  mutate(ob_gravidity = as.factor(ob_gravidity)) %>% 
  mutate(ob_parity = as.character(ob_parity)) %>% 
  mutate(ob_parity = as.factor(ob_parity)) %>% 
  mutate(ob_multiple_births = as.character(ob_multiple_births)) %>% 
  mutate(ob_multiple_births = as.factor(ob_multiple_births)) %>% 
  filter(delivery_method != 'Other') %>% 
  mutate(delivery_method = as.character(delivery_method)) %>% 
  mutate(delivery_method = as.factor(delivery_method)) %>% 
  mutate(ob_gravidity = factor(ob_gravidity, levels = c(1,
                                                        2,
                                                        3,
                                                        4,
                                                        5,
                                                        6,
                                                        7,
                                                        8,
                                                        9,
                                                        10,
                                                        11,
                                                        12,
                                                        13,
                                                        14,
                                                        15,
                                                        16,
                                                        17,
                                                        18))) %>% 
  mutate(ob_parity = factor(ob_parity, levels = c(1,
                                                  2,
                                                  3,
                                                  4,
                                                  5,
                                                  6,
                                                  7,
                                                  8,
                                                  9,
                                                  10,
                                                  11,
                                                  12)))
```

```{r}
final_df %>% 
  select(mom_age_at_del,
         mom_race,
         mom_ethnicity,
         mom_marital_status,
         employment_status,
         preeclampsia,
         pregest_dm,
         gestational_dm,
         placental_abruption,
         maternal_dvt,
         gest_age_wks,
         delivery_method,
         ob_gravidity,
         ob_parity,
         ob_multiple_births,
         baby_count,
         mean_pre_bmi,
         mean_post_bmi,
         bmi_return
  ) %>% 
  tbl_summary(
    by = bmi_return,
    missing_text = 'Missing'
  ) %>%
  add_p() %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels() 
```

```{r}
unweighted_mod <- glm(
   post_htn ~ 
    bmi_return +
    mom_age_at_del +
    mom_race +
    mom_ethnicity +
    mom_marital_status +
    employment_status +
    preeclampsia +
    pregest_dm +
    gestational_dm +
    placental_abruption +
    #maternal_dvt #+ # not enough obs
    gest_age_wks +
    delivery_method +
    ob_gravidity +
    ob_parity +
    ob_multiple_births +
    baby_count +
    mean_pre_bmi
    #mean_post_bmi not converging
  ,
  data = final_df,
  family = binomial(link = "logit")) 

summary(unweighted_mod)

unweighted_mod2 <- glm(
  post_htn ~ 
    bmi_return +
    mom_age_at_del +
    mom_race +
    mom_ethnicity +
    mom_marital_status +
    employment_status +
    preeclampsia +
    pregest_dm +
    gestational_dm +
    placental_abruption +
    #maternal_dvt #+ # not enough obs
    gest_age_wks +
    delivery_method +
    ob_gravidity +
    ob_parity +
    ob_multiple_births +
    baby_count +
    mean_pre_bmi
    #mean_post_bmi not converging
  ,
  data = unweighted_mod$model,
  family = binomial(link = "logit")) 

step_unweight2 <- step(unweighted_mod2)
summary(step_unweight2)
tbl_regression(step_unweight2, exponentiate = T)
```

data dictionary:

**patient_num**: *integer* unique to each patient

**dx_code**: *character* ICD-10 code for the diagnosis of hypertension if applicable, I10

**htn_dx_date**: *date* shifted date of patient diagnosis of hypertension if applicable, shifted by $\pm$ 10 days

**pre_htn**: *factor* yes if patient was diagnosed w/ hypertension before 12 months post-delivery, no if not

**post_htn**: *factor* yes if patient was diagnosed w/ hypertension between 13-72 months post-delivery, no if not

**mom_admit_dttm_shifted**: *date* date of the mother's delivery admission

**mom_disch_dttm_shifted**: *date* date of the mother's delivery discharge

**mom_los**: *integer* mom's length of stay in days for the delivery encounter

**mom_age_at_del**: *date* mom's age at delivery in years

**mom_marital_status**: *factor* mom's current marital status: Divorced, Married, Other, Single

**mom_race**: *factor* mom's current race: Black or African American, Other, White or Caucasian

**mom_ethnicity**: *factor* mom's current ethnicity: Hispanic, NH (non-hispanic), Other

**mom_wt_oz**: *numeric* most recent mother weight up to delivery

**mom_bmi**: *numeric* most recent mother BMI up to delivery

**preeclampsia**: *factor* indicates presence of a preeclampsia diagnosis on the
delivery encounter

**pregest_dm**: *factor* indicates presence of a pregestational diabetes diagnosis
on the delivery encounter

**gestational_dm**: *factor* indicates presence of a gestational diabetes diagnosis on
the delivery encounter

**placental_abruption**: *factor* indicates presence of a placental abruption diagnosis on
the delivery encounter

**maternal_dvt**: *factor* indicates presence of a maternal deep vein thrombosis
diagnosis on the delivery encounter

**baby_patient_num**: *integer* Masked MRN, the i2b2 patient number

**baby_yob_shifted**: *date* Baby's year of birth 

**baby_dob_shifted**: *date* Baby's date of birth

**baby_dod_shifted**: *date* Baby's date of death

**baby_admit_dttm_shifted**: *date* Date of the baby's birth admission

**baby_disch_dttm_shifted**: *date* Date of the baby's birth discharge

**baby_birth_ht_in**: *numeric* Baby's birth height in inches

**baby_birth_wt_oz**: *numeric* Baby's birth weight in ounces

**baby_birth_wt_gms**: *numeric* Baby's birth weight in grams

**gest_age_wks**: *numeric* Baby's gestational age in weeks and days divided 7

**delivery_method**: *factor* Name of the delivery method used for the birth: C-Section, Operative Vaginal, Vaginal, Other (not included in analyses)

**baby_sex**: *factor* baby's current sex, male or female

**baby_race**: *factor* baby's current race: Black or African American, Other, White or Caucasian

**baby_ethnicity**: *factor* baby's current ethnicity: Hispanic, NH (non-hispanic), Other

**ob_gravidity**: *factor* Number of pregnancies documented on the first OB visit
up to 90 days after the delivery

**ob_parity**: *factor* Number of viable offspring documented on the first OB
visit up to 90 days after the delivery

**ob_multiple_births**: *factor* Number of multiple births documented on the first OB
visit up to 90 days after the delivery

**mom_ht_cm**: *numeric* mom's height in centimeters

**baby_count**: *integer* number of babies birthed in most recent birth

**diff_htn**: *numeric* number of days between diagnosis of hypertension and baby DOB

**measure_date_shifted**: *date* date of mom's BMI measurement

**highest_diastolic**: *numeric* mom's diastolic component of highest blood pressure up to delivery

**highest_systolic**: *date* mom's systolic component of highest blood pressure up to delivery

**post_bmi_date**: *date* date of post-delivery BMI measurement

**pre_bmi_date**: *date* date of pre-delivery BMI measurement

**mean_pre_bmi**: *numeric* averaged BMI measured pre-delivery

**mean_post_bmi**: *numeric* averaged BMI measured post-delivery

**birth_date_shifted**: *date* mom's birth date

**employment_status**: *factor* mom's current employment status: Full Time, Part Time, Not Employed, Other

**bmi_return**: *factor* yes if mom returned to pre-delivery BMI, no if post-delivery BMI was at least 1 point higher than pre-delivery BMI